Short-term synaptic and neuronal plasticity act in synergy for deviance detection in spiking networks

### 2022-12-12 paper-1/manuscript.tex
Update v -> V_m

We modeled neurons as leaky integrate-and-fire units whose membrane potential $v$ at time $t$ followed
\begin{equation}
    \tau_m \frac{dv}{dt} = (v_{rest}-v) + I_{syn}(t)
\end{equation}
with $tau_m = 30$~ms the membrane time constant and $v_{rest} = -60$~mV the resting membrane potential. Synaptic currents were modeled in a conductance-based manner, following
\begin{equation}
    I_{syn} &= g_e(E_e-v) + g_i(E_i-v)
\end{equation}
with $E_e = 0$~mV and $E_i = -100$~mV the excitatory and inhibitory reversal potentials, respectively. Synaptic conductances evolved according to
\begin{align} 
    \tau_e \frac{dg_e}{dt} &= -g_e + \sum_{j \in \boldsymbol E} U x_j w \delta(t - \hat{t_j}) \nonumber \\
    \tau_i \frac{dg_i}{dt} &= -g_i + \sum_{j \in \boldsymbol I} w \delta(t - \hat{t_j}) \label{eqn-gsyn}
\end{align}
with $\tau_e = 2$~ms the excitatory time constant, echoing AMPA receptor dynamics \citep{Hausser1997-cn}, $\tau_i = 4$~ms the inhibitory time constant, echoing GABA-A receptor dynamics \citep{Destexhe1994-oc}, $\boldsymbol E$ and $\boldsymbol I$ the sets of presynaptic excitatory and inhibitory neurons, respectively, $w$ the synaptic weight, $\delta(\cdot)$ the Dirac delta function, and $\hat{t}$ the spike times.

@@

When a neuron's membrane potential reached the firing threshold $v_\theta$, a spike was emitted, and the potential was clamped to $v = v_{reset} = -74$~mV for a fixed refractory period of 3~ms (excitatory neurons). Inhibitory neurons were modeled as fast-spiking cells with a refractory period of 2~ms and a constant firing threshold $v_\theta = \theta_0 = -54$~mV \refp{Mensi2012-au}. In contrast, excitatory neurons were modeled with threshold adaptation (TA) as in \cite{Teeter2018-iz}, following
\begin{align}
    v_\theta &= \theta_0 + V_{TA}(t) \nonumber \\
    \tau_{\theta} \frac{dV_{TA}}{dt} &= -V_{TA} + \hat{\theta} \delta(t - \hat{t}) \label{eqn-TA}
\end{align}
with increment $\hat{\theta} = 1$~mV and decay time constant $\tau_{\theta} = 1$~s \refp{Pozzorini2015-ei}.

>>>>

We modeled neurons as leaky integrate-and-fire units whose membrane potential $V_m$ at time $t$ followed
\begin{equation}
    \tau_m \frac{dV_m}{dt} = (v_{rest}-V_m) + I_{syn}(t)
\end{equation}
with $tau_m = 30$~ms the membrane time constant and $v_{rest} = -60$~mV the resting membrane potential. Synaptic currents were modeled in a conductance-based manner, following
\begin{equation}
    I_{syn} = g_e(E_e-V_m) + g_i(E_i-V_m)
\end{equation}
with $E_e = 0$~mV and $E_i = -100$~mV the excitatory and inhibitory reversal potentials, respectively. Synaptic conductances evolved according to
\begin{align} 
    \tau_e \frac{dg_e}{dt} &= -g_e + \sum_{j \in \boldsymbol E} U x_j w \delta(t - \hat{t_j}) \nonumber \\
    \tau_i \frac{dg_i}{dt} &= -g_i + \sum_{j \in \boldsymbol I} w \delta(t - \hat{t_j}) \label{eqn-gsyn}
\end{align}
with $\tau_e = 2$~ms the excitatory time constant, echoing AMPA receptor dynamics \citep{Hausser1997-cn}, $\tau_i = 4$~ms the inhibitory time constant, echoing GABA-A receptor dynamics \citep{Destexhe1994-oc}, $\boldsymbol E$ and $\boldsymbol I$ the sets of presynaptic excitatory and inhibitory neurons, respectively, $w$ the synaptic weight, $\delta(\cdot)$ the Dirac delta function, and $\hat{t}$ the spike times.

@@

When a neuron's membrane potential reached the firing threshold $v_\theta$, a spike was emitted, and the potential was clamped to $V_m = v_{reset} = -74$~mV for a fixed refractory period of 3~ms (excitatory neurons). Inhibitory neurons were modeled as fast-spiking cells with a refractory period of 2~ms and a constant firing threshold $v_\theta = \theta_0 = -54$~mV \refp{Mensi2012-au}. In contrast, excitatory neurons were modeled with threshold adaptation (TA) as in \cite{Teeter2018-iz}, following
\begin{align}
    v_\theta &= \theta_0 + V_{TA}(t) \nonumber \\
    \tau_{\theta} \frac{dV_{TA}}{dt} &= -V_{TA} + \hat{\theta} \delta(t - \hat{t}) \label{eqn-TA}
\end{align}
with increment $\hat{\theta} = 1$~mV and decay time constant $\tau_{\theta} = 1$~s \refp{Pozzorini2015-ei}.
